---
title: "Leaflet on R Notes"
author: "Zuoling"
output:
  html_notebook: default
---
```{r}
library(leaflet)
```

---

leaflet function creates a map widget that you can store in a varible so that you can modify the map later on, you can add layer to the map using the pipe operator (```%>%```)


## Basic Operation
- First of all, create a map widget by calling ```leaflet()```
- Adding layers by functions like ```addTiles()``` and  ```addMarkers()```

```{r}
my_map <- leaflet() %>%
  # addTiles() calling map from OSM
  addTiles()  


my_map <- leaflet() %>% 
  # or can use tiles providers
  addProviderTiles("Thunderforest.TransportDark")
```

<br>

We use function ```addMarkers()``` to add marker, which is a single point 

```{r}
## Adding Markers 
my_map <- my_map %>%
  addMarkers(lat = 39.2980803, lng= -76.5898801,
             popup = "FL's Office")

```

## Combine with HTML feature 

Leaflet works very well with html, below is the example


```{r}
GICLinks <- c(
  "<a href = 'http://www.gic.com.sg/'> GIC </a>",
  "<a href = 'http://www.gic.com.sg/newsroom'> GIC NewsRoom </a>",
  "<a href = 'http://www.gic.com.sg/newsroom?id=680&Itemid=159'> News </a>"
)


num_of_link <- 3

df <- data.frame(lat = runif(num_of_link, min = 1.294, max = 1.296),
                 lng = runif(num_of_link, min = 103.77, max = 103.78))

df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup = GICLinks)
```

Here is another HTML example, play with popup parameter 

```{r}
# create dataframe 
data <- data.frame(
  c(43.11940, 43.11940),
  c(-79.24658, -79.244658),
  c("HQ1","HQ2"),
  c(4736583, 3204853),
  c('<iframe width="300" height="169" 
    src="https://www.youtube.com/embed/vl9D3uTk36k?showinfo=0" frameborder="0" allowfullscreen></iframe>',
    
    '<iframe width="300" height="169" 
    src="https://www.youtube.com/embed/dBk8gGX1MNk?showinfo=0" frameborder="0" allowfullscreen></iframe>')
)

colnames(data) <- c("lat", "lng", "name","score","video")

names(data) <- c("lat", "lng", "name","score","video")

map <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(data = data, lat = ~lat, lng = ~lng, 
             popup = ~paste(
               "<h3 style = 'color: red' >", name ,"</h3>", 
               "<b>Score:</b>", score, "<br>",
               video,
               sep = " ")) %>% 
  
  # setview function 
  setView(lat  = 43.11931, lng  = -79.24611, zoom = 13)

map 
```



---
---

## Clustering / Representation


### Clustering 

We can do simple points clustering with ```markerClusterOptions()```
```{r}
num_of_link <- 500
df <- data.frame(lat = runif(num_of_link, min = 1.2738, max = 1.278),
                 lng = runif(num_of_link, min = 103.845, max = 103.850))

df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())

```


### Circle 
We can use ```addCircles()``` and its radius parameter to do the numerical representation
```{r}
num_of_link <- 10 

md_cities <- data.frame(name = c("Baltimore", "Frederick","Rockville","Gaithersburg", "Bowie",
                                 "Hagerstown","Annapolis","College Park", "Salibury", "Laurel"),
                        pop = c(619493, 66169, 62334, 61045, 55243,
                               39890, 38880,30587, 30484, 25346),
                        lat = c(39.2920592, 39.4143921, 39.0840, 39.1434, 39.0068,
                                39.6418, 38.9784, 38.9897, 38.3607, 39.0993),
                        lng = c(-76.6077852, -77.4204875, -77.1528, -77.2014, -76.7791,
                                    -77.7200, -76.4922, -76.9378, -75.5994, -76.8483))

md_cities %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircles(weight = 1, radius = sqrt(md_cities$pop) * 30)
```



### Legend
We can add legend by ```addLegend()``` function 
```{r}
df <- data.frame(lat = runif(20, min = 39.25, max = 39.35),
                 lng = runif(20, min = -76.65, max = -76.55),
                 col = sample(c("red","blue","green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)


df %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(color = df$col) %>% 
  addLegend(labels = LETTERS[1:3], colors = c("red","blue","green"))
```

## Some Good thing to have feature 

---

### Adding custom icon 
```{r}
GICIcon <- makeIcon(
  iconUrl = "http://www.gic.com.sg/templates/gic/images/site/gic-logo.png",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2 , iconAnchorY = 16
)

df %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(icon = GICIcon, lat = ~lat, lng = ~lng)
```


